\section{Group Members Contribution}

% For each group member, describe in detail the contribution to the project.

\begin{description}
	\item[Busato Nicola] Writing and image creation of Chapter 4 and ideation of the REST API. Set up project and Docker configuration for a Tomcat and a PostgreSQL container. Developed /user/signup, /user/login and /user/logout (jsp, servlet, css, js and sql access) and GameSettingsServlet.
    \item[Cini Jacopo]
    Helped to develop GameDispatcherServlet, which then uses two REST APIs: /lupus/game/logs/\{gameID\} and /lupus/game/logs/\{gameID\}/master. Developed GameLog rest resource, its respective DAO which is GetActionByIdGameDAO and its resource, the class Action. Contribuited to write section 5 of this document.
    \item[Miele Riccardo] With Nicola Busato has brainstormed ideas for the project and sketched out an outline to start developing the project. Has set up the database by creating the ER scheme, the logic scheme and the implementation in SQL. Has written the chapter 3 explaining all the entities and the relations contained in the ER and logic schemes.
    \item[Gusella Michele] Helped to develop GameDispatcherServlet, which then uses two REST APIs: /game/players/\{gameID\} and /game/players/\{gameID\}/master. Developed GamePlayers rest resource, its respective DAO which is GetGamePlayersDAO and its resource, the class PlaysAsIn. Contribuited to write section 5 of this document.
    \item[Miele Riccardo] With Nicola Busato has brainstormed ideas for the project and sketched out an outline to start developing the project. Has set up the database by creating the ER scheme, the logic scheme and the implementation in SQL. Has written the chapter 3 explaining all the entities and the relations contained in the ER and logic schemes.
    Has developed RR for statistic and logs (with DAOs and the necessary resources). Has revised and fixed the chapter 2.
	\item[Momesso Jacopo] Developed the UserDispatcher and UserFilter, the RestResources related to /user/me and /user/\{username\}, the RulesServlet for handling the rules page and the roles of the game, the GameActionsPostRR, in particular the night phase controls for each action and for each role, and all the relatives DAO for querying the database. Wrote chapter 1 of this document with the goals of the project and the rules of the game Lupus in Fabula.
    \item[Pozzo Nicola] Developed the /User/me/friend in
\end{description}
